\chapter{攻读学位期间的成果}

\begin{itemize}
	\setlength{\itemsep}{5pt}
	% \setlength{\parsep}{2em}
	
	\item \textbf{\heiti\sihao{论文}}
	      \begin{enumerate}
	      	\setlength{\itemsep}{-\itemsep}  %调整间距
	      	% \usecounter{numcount} % 使用计数器,初始值为0
	      	% \setlength{\leftmargin}{3em} %左边界
	      	% \setlength{\parsep}{-0.5ex} %段落间距
	      	% \setlength{\topsep}{-10ex} %列表到上下文的垂直距离
	      	% \setlength{\itemsep}{0.5ex} %条目间距
	      	% \setlength{\labelsep}{0.3em} %标号和列表项之间的距离,默认0.5em
	      	% \setlength{\itemindent}{1.1em} %标签缩进量
	      	% \setlength{\listparindent}{0em} %段落缩进量
	      	
	      	\item \textbf{Mengxing Dong}, Bowei Zou, Jin Qian, Rongtao Huang, Yu Hong. 2021.
	      	      ThinkTwice: A Two-Stage Method for Long-Text Machine Reading Comprehension.
	      	      In Proceedings of NLPCC, pages 427-438, Qingdao, China. (CCF-C类会议)
	      	      
	      	\item \textbf{Mengxing Dong}, Bowei Zou, Yanling Li, Yu Hong. 2023.
	      	      CoLISA: Inner Interaction via Contrastive Learning for Multi-Choice Reading Comprehension.
	      	      In Proceedings of ECIR, pages 264-278, Dublin, Ireland. (CCF-C类会议)
	      	      
	      	\item Jin Qian, Bowei Zou, \textbf{Mengxing Dong}, Xiao Li, Ai Ti Aw, Yu Hong. 2022.
	      	      Capturing Conversational Interaction for Question Answering via Global History Reasoning.
	      	      In Proceedings of NAACL, Online. (CCF-B类会议)
	      	      
	      	\item Xibo Li, Bowei Zou, \textbf{Mengxing Dong}, Jianmin Yao, Yu Hong. 2022.
	      	      Concession-First Learning and Coarse-to-Fine Retrieval for Open-Domain Conversational Question Answering.
                  In Proceedings of ICTAI, Online. (CCF-C类会议)
			
			\item Yanling Li, Bowei Zou, Yifan Fan, \textbf{Mengxing Dong}, Yu Hong. 2023.
				  Coreference-Aware Double-Channel Attention Network for Multi-Party Dialogue Reading Comprehension.
				  In Proceedings of IJCNN, Queensland, Australia. (CCF-C类会议)

	      	      
	      \end{enumerate}
	      
	% \item \textbf{\heiti\sihao{比赛}}
	%       \begin{enumerate}
	%       	\item 2021语言与智能技术竞赛：机器阅读理解任务，优秀奖.
	%       \end{enumerate}
	      
	\item \textbf{\heiti\sihao{实习}}
	      \begin{enumerate}
	      	\item \textsc{2021/8--2022/1}. 北京-百度-搜索策略部.
	      \end{enumerate}
	      
\end{itemize}
